### 2022-11-15 NSF2022/Description/summary.tex

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of granules. The main
ingredient is a nonlocal interaction through the solution of an moving
domain elliptic PDE that encompasses long-range amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-known vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
amphiphilic ensembles, improving on mathematical models, efficient,
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory for the collective dynamics.

>>>>

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of granules with non-uniform hydrophobicity on their boundaries. The main
ingredient is a nonlocal interaction through the solution of an moving
domain elliptic PDE that encompasses long-range amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the mathematical in distinguished limits to make connection with continuum model,
designing efficient,
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory to quantify the ratio of polar to nematic components in the collective dynamics.
